### 2018-01-20 manuscript.rmd
fixed typos, formatting

Siphonophores remain poorly known, in large part because they are fragile and difficult to collect. They have, however, been of great interest for more than 150 years in part due to their unique structure and development [@mapstone2014global;@mackie1987siphonophore]. Like many other cnidarians, they are colonial: they grow by incomplete asexual reproduction. Each colony arises from a single embryo that forms the protozooid, the first body. One or two growth zones (Fig. 2) then arise that asexually produce other genetically identical zooids that remain attached [@carre1969etude; @carre1991complete; @carre1967; @carre1995ordre]. These zooids are each homologous to a solitary animal, but are physiologically integrated [@totton1965synopsis; @mackie1987siphonophore; @dunn2006evolution]. Siphonophores differ significantly from other colonial animals in colony structure, development, and the high degree to which their zooids are functionally specialized and arranged in precise, repeating, species-specific patterns [@Beklemishev1969;@cartwright2010character]. The functions that zooids are specialized for include feeding, reproducing, or swimming (Fig. 2) [@dunn2006evolution].

@@

![Schematic of the siphonophore *Nanomia bijuga*, orientated with the anterior of the colony at the top of the page, and the ventral side to the left. Adapted from http://commons.wikimedia.org/wiki/File:Nanomia_bijuga_whole_animal_and_growth_zones.svg, drawn by Freya Goetz. (A) Overview of the whole mature colony. (B) Inset of the pneumatophore and nectosomal growth zone. A series of buds gives rise to nectophores. (C) Inset of the siphosomal growth zone. Probuds subdivide to give rise to zooids in repeating-units (cormidia). The gastrozooid (specialized feeding polyp) is the posterior-most zooid within each cormidium.](figures/Figure2.pdf)

@@

## 3.2 Character Evolution
```{r char_evo_setup, include=F, echo=F}
#Load data
read.csv('character_coding/main_characters.csv', header = T, sep = ',') -> cdata
rownames(cdata) = cdata$Species

@@

```{r simmap_making, echo=F, message=F, warning=F, include=F}
#Stochastic trait mapping:
#Make simmap objects
#print("SIMMAP Sex Distribution")
make.simmap(ultratree, sex, nsim = 100, message=FALSE) -> sex_sim
#print("SIMMAP Palpons")
make.simmap(ultratree, palpons, nsim = 100, message=FALSE) -> palpons_sim
#print("SIMMAP Tentilla")
make.simmap(ultratree, tentilla, nsim = 100, message=FALSE) -> tentilla_sim
#print("SIMMAP Tentilla2")
make.simmap(ultratree, tentilla2, nsim = 100, message=FALSE) -> tentilla_sim2
#print("SIMMAP Nectosome")
make.simmap(ultratree, nectosome, nsim = 100, message=FALSE) -> nectosome_sim
#print("SIMMAP Nectosome Position")
make.simmap(ultratree, bracts, nsim = 100, message=FALSE) -> bracts_sim
#print("SIMMAP Habitat")

@@

```{r sex, echo=F, message=F, warning=F, include=F}
par(ask=F)
#Simmap SEX
plotTree(ultratree, lwd = 4)
colors = c("black", "red")
names(colors) = c("Dioecious", "Monoecious")
sex_sim %>% plotSimmap(lwd = 4, add = T, colors=colors)
nodelabels(pie=(describe.simmap(sex_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
sex_obj <- densityMap(sex_sim, plot=FALSE)
sex_obj$cols[1:length(sex_obj$cols)]<-colorRampPalette(colors=c("#4A4ACC", "orange"), space="Lab")(length(sex_obj$cols))
 pdf("figures_raw/figure_5_raw_sex.pdf")
 plot(sex_obj)
 dev.off()
```

```{r palpons, echo=F, message=F, warning=F, include=F}
#Simmap PALPONS

@@

```{r vars_plot, echo=F, message=F, warning=F, include=F}
#Get Raw Data
raw_data = read.csv(file="character_coding/trim_siphdepths.tsv", sep = "\t")[,c(4,3,5:11)]
raw_data = raw_data[order(raw_data$ConceptName),]

@@

```{r ggtree_bin_heatmap, echo=F, message=F, warning=F, include=F}
p <- ggtree(ultratree)
p <- p + geom_tiplab(size=2.2)
f_cdata = sapply(cdata, as.factor) %>% as.data.frame %>% .[c(1,2,5:9,17,18,3)]
rownames(f_cdata) = rownames(cdata)
f_cdata = f_cdata[,c(7,4,1,3,6,2,10,8,9,5)]
f_cdata[match(tree$tip.label,rownames(f_cdata)),]

@@

Ancestral character state reconstructions favor the hypothesis that monoecy arose twice (Fig. 5A), once in Calycophorae and once in Clade A. This is consistent with differences in the arrangements of male and female gonophores in the two clades. In Clade A, male and female zooids are found within the same cormidium (a single reiterated sequence of zooids along the stem, see Fig. 2). In these species, the male and female zooids are placed at very different but well defined locations within the cormidium. Meanwhile in calycophorans, each cormidium bears either male or female gonophores. In this form of monoecy, the male and female cormidia can either be in an alternating pattern, or there can be several male or female cormidia in a row. In either case, male and female zooids are found at the same corresponding locations within the cormidia. In sum, homoplasy in sexual system evolution along with variation in the spatial arrangement of gonophores within a colony suggest that siphonophores have evolved different ways to be monoecious. Both Calycophorae and Clade A both have a large proportion of shallow water species (see section 3.7), suggesting that there may be an association between habitat depth and sexual mode. Similar independent transitions from gonochorism (separate sex) to hermaphrodism (both sexes in the same individual) have been identified in shallow-water scleractinian corals (Anthozoa, Cnidaria) [@kerr2011correlated]. To test this hypothesis, a more extensive taxon sampling of the Calycophorae is needed.

@@

![Stochastic mapping reconstruction of the evolutionary history of A) distribution of sexual zooids on the colonies, and B) palpon zooids. The color gradients show the reconstructed probability estimate of the discrete character states along the branches. Intermediate values reflect uncertainty.](figures/Figure5.pdf)

@@

@@

```{r summary_table, results='asis', echo=FALSE, comment=NA, warning=FALSE}

####The supplementary table is too long. We decided to include as a supplementary datafile instead

#	summary_stats = read.table("supplementary_info/Library_summary.csv", header=TRUE, sep=",")
#	names(summary_stats)<-c("Species","Mean insert size (bp)","Insert size sd","# read pairs","% kept after rRNA removal","% kept after assembly","Adapter fails","Quality fails","Base Comp. fails","Total transcripts","Coding transcripts")

#xtable_summary<-xtable(summary_stats, caption="Supplementary table 1.The assembly summary statistics for all included taxa, showing mean insert size, and the percentage of reads kept after pipeline steps.")
#align( xtable_summary ) <- c('l|','p{0.8in}','p{0.3in}','p{0.3in}','p{0.5in}','p{0.3in}','p{0.3in}','p{0.4in}','p{0.5in}','p{0.5in}','p{0.5in}','p{0.5in}')
#print(xtable_summary,include.rownames=FALSE,comment=F, floating =FALSE, tabular.environment = "longtable")

@@

#####Stochastic Character maps
```{r tentilla, echo=F, message=F,warning=F, fig.width=6.5, fig.height=7, fig.cap= "Stochastic character map of presence of tentilla with *Physalia* included as not bearing tentilla."}
#Simmap TENTILLA
# plotTree(ultratree, lwd = 4)
# colors = c("black", "red")
# names(colors) = c("Absent", "Present")
# tentilla_sim %>% plotSimmap(lwd = 4, add = T,colors=colors)
# nodelabels(pie=(describe.simmap(tentilla_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
# add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
tentilla_obj <- densityMap(tentilla_sim,plot=FALSE)
tentilla_obj$cols[1:length(tentilla_obj$cols)]<-colorRampPalette(colors=c("#4A4ACC", "orange"), space="Lab")(length(tentilla_obj$cols))
plot(tentilla_obj)
```

```{r tentilla2, echo=F, message=F, warning=F, fig.width=6.5, fig.height=7, fig.cap= "Stochastic character map of presence of tentilla with *Physalia* included as bearing tentilla."}
#Simmap TENTILLA
# plotTree(ultratree, lwd = 4)
# colors = c("black", "red")
# names(colors) = c("Absent", "Present")
# tentilla_sim2 %>% plotSimmap(lwd = 4, add = T,colors=colors)
# nodelabels(pie=(describe.simmap(tentilla_sim2, plot=F)$ace) ,piecol=colors,cex=0.35)
# add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
tentilla2_obj <- densityMap(tentilla_sim2, plot=FALSE)
tentilla2_obj$cols[1:length(tentilla2_obj$cols)]<-colorRampPalette(colors=c("#4A4ACC", "orange"), space="Lab")(length(tentilla2_obj$cols))
plot(tentilla2_obj)
```

```{r nectosome, echo=F, message=F, warning=F,  fig.width=6.5, fig.height=7, fig.cap= "Stochastic character map of presence of nectosome."}
#Simmap NECTOSOME
# plotTree(ultratree, lwd = 4)
# colors = c("black", "red")
# names(colors) = c("Absent", "Present")
# nectosome_sim %>% plotSimmap(lwd = 4, add = T,colors=colors)
# nodelabels(pie=(describe.simmap(nectosome_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
# add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
nectosome_obj <- densityMap(nectosome_sim, plot=FALSE)
nectosome_obj$cols[1:length(nectosome_obj$cols)]<-colorRampPalette(colors=c("#4A4ACC", "orange"), space="Lab")(length(nectosome_obj$cols))
plot(nectosome_obj)
```

```{r desc_mantle, echo=F, message=F, warning=F,  fig.width=6.5, fig.height=7, fig.cap= "Stochastic character map of presence of a descending mantle canal in the nectophores. Cystonects and Athorybia were excluded as they do not have a nectosome. "}
#Simmap Descending Mantle Canal
# plotTree(ultratree, lwd = 4)
# colors = c("black", "red")
# names(colors) = c("Absent", "Present")
# desc_mantle_sim %>% plotSimmap(lwd = 4, add = T,colors=colors)
# nodelabels(pie=(describe.simmap(desc_mantle_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
# add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
desc_mantle_obj <- densityMap(desc_mantle_sim, plot=FALSE)
desc_mantle_obj$cols[1:length(desc_mantle_obj$cols)]<-colorRampPalette(colors=c("#4A4ACC", "orange"), space="Lab")(length(desc_mantle_obj$cols))
plot(desc_mantle_obj)
```

```{r nectosome_pos, echo=F, message=F, warning=F,  fig.width=6.5, fig.height=7, fig.cap= "Stochastic character map for the evolution of the position of the nectosome. Cystonects were excluded as they do not have a nectosome."}
#SIMMAP NectoPos
# plotTree(ultratree, lwd = 4)
# colors = c("black", "red")
# names(colors) = c("Dorsal", "Ventral")
# necto_pos_sim %>% plotSimmap(lwd = 4, add = T)
# nodelabels(pie=(describe.simmap(necto_pos_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
# add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
necto_pos_obj <- densityMap(necto_pos_sim, plot=FALSE)
necto_pos_obj$cols[1:length(necto_pos_obj$cols)]<-colorRampPalette(colors=c("#4A4ACC", "orange"), space="Lab")(length(necto_pos_obj$cols))
plot(necto_pos_obj)
```

```{r median_cont, echo=F, message=F, warning=F, fig.width=6.5, fig.height=7, fig.cap= "Brownian Motion character map of median depth of species observed with an MBARI ROV."}
depth_value = depth_median
depthmap <- contMap(dpruned_tree, depth_value, plot=F) %>% setMap(colors=c("cyan","blue","black"))
plot(depthmap)
```

```{r median_depth_extended, echo=F, message=F, warning=F, fig.width=6.5, fig.height=7, fig.cap= "Brownian Motion character map of median depth of species including blue water diving observations." }

fitContinuous(ultratree, median_extended, model="white")$opt$aicc
fitContinuous(ultratree, median_extended, model="BM")$opt$aicc
fitContinuous(ultratree, median_extended, model="OU")$opt$aicc

```{r phylosig_binaries, results='asis',echo=F, message=F, warning=F}
 # make it xtable
binaries_phylosig = multiPhylosignal(as.matrix(cdata[,c(2,5:8)]), ultratree)
names(binaries_phylosig)<-c("K","PICvar obs","PICvar rnd","P-value","Z-score")
xtable_PS<-xtable(binaries_phylosig,auto=TRUE, caption="Phylogenetic signal in the binary traits, including Blomberg's K statistic, the mean observed PIC variance, the random variance of PICs, p-value of the comparison of observed and random variance, and the z-score. ")
print(xtable_PS,comment=F)

>>>>

Siphonophores remain poorly known, in large part because they are fragile and difficult to collect. They have, however, been of great interest for more than 150 years due to their unique structure and development [@mapstone2014global;@mackie1987siphonophore]. Like many other cnidarians, they are colonial: they grow by incomplete asexual reproduction. Each colony arises from a single embryo that forms the protozooid, the first body. One or two growth zones (Fig. 2) then arise that asexually produce other genetically identical zooids that remain attached [@carre1969etude; @carre1991complete; @carre1967; @carre1995ordre]. These zooids are each homologous to a solitary animal, but are physiologically integrated [@totton1965synopsis; @mackie1987siphonophore; @dunn2006evolution]. Siphonophores differ significantly from other colonial animals in terms of colony structure and development -- their zooids are highly functionally specialized and arranged in precise, repeating, species-specific patterns [@Beklemishev1969;@cartwright2010character]. The functions that zooids are specialized for include feeding, reproducing, or swimming (Fig. 2) [@dunn2006evolution].

@@

![Schematic of the siphonophore *Nanomia bijuga*, orientated with the anterior of the colony at the top of the page, and the ventral side to the left. Adapted from http://commons.wikimedia.org/wiki/File:Nanomia_bijuga_whole_animal_and_growth_zones.svg, drawn by Freya Goetz. (A) Overview of the whole mature colony. (B) Inset of the pneumatophore and nectosomal growth zone. A series of buds give rise to nectophores. (C) Inset of the siphosomal growth zone. Probuds subdivide to give rise to zooids in repeating-units (cormidia). The gastrozooid (specialized feeding polyp) is the posterior-most zooid within each cormidium.](figures/Figure2.pdf)

@@

## 3.2 Character Evolution
```{r char_evo_setup, include=F, echo=FALSE}
#Load data
read.csv('character_coding/main_characters.csv', header = T, sep = ',') -> cdata
rownames(cdata) = cdata$Species

@@

```{r simmap_making, echo=FALSE, message=FALSE, warning=FALSE, include=F}
#Stochastic trait mapping:
#Make simmap objects
#print("SIMMAP Sex Distribution")
make.simmap(ultratree, sex, nsim = 100, message=FALSE) -> sex_sim
#print("SIMMAP Palpons")
make.simmap(ultratree, palpons, nsim = 100, message=FALSE) -> palpons_sim
#print("SIMMAP Tentilla")
make.simmap(ultratree, tentilla, nsim = 100, message=FALSE) -> tentilla_sim
#print("SIMMAP Tentilla2")
make.simmap(ultratree, tentilla2, nsim = 100, message=FALSE) -> tentilla_sim2
#print("SIMMAP Nectosome")
make.simmap(ultratree, nectosome, nsim = 100, message=FALSE) -> nectosome_sim
#print("SIMMAP Nectosome Position")
make.simmap(ultratree, bracts, nsim = 100, message=FALSE) -> bracts_sim
#print("SIMMAP Habitat")

@@

```{r sex, echo=FALSE, message=F, warning=FALSE, include=F}
par(ask=F)
#Simmap SEX
plotTree(ultratree, lwd = 4)
colors = c("black", "red")
names(colors) = c("Dioecious", "Monoecious")
sex_sim %>% plotSimmap(lwd = 4, add = T, colors=colors)
nodelabels(pie=(describe.simmap(sex_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
sex_obj <- densityMap(sex_sim, plot=FALSE)
sex_obj$cols[1:length(sex_obj$cols)]<-colorRampPalette(colors=c("#4A4ACC", "orange"), space="Lab")(length(sex_obj$cols))
 pdf("figures_raw/figure_5_raw_sex.pdf")
 plot(sex_obj)
 dev.off()
```

```{r palpons, echo=FALSE, message=F, warning=FALSE, include=F}
#Simmap PALPONS

@@

```{r vars_plot, echo=FALSE, message=F, warning=FALSE, include=F}
#Get Raw Data
raw_data = read.csv(file="character_coding/trim_siphdepths.tsv", sep = "\t")[,c(4,3,5:11)]
raw_data = raw_data[order(raw_data$ConceptName),]

@@

```{r ggtree_bin_heatmap, echo=FALSE, message=F, warning=FALSE, include=F}
p <- ggtree(ultratree)
p <- p + geom_tiplab(size=2.2)
f_cdata = sapply(cdata, as.factor) %>% as.data.frame %>% .[c(1,2,5:9,17,18,3)]
rownames(f_cdata) = rownames(cdata)
f_cdata = f_cdata[,c(7,4,1,3,6,2,10,8,9,5)]
f_cdata[match(tree$tip.label,rownames(f_cdata)),]

@@

Ancestral character state reconstructions favor the hypothesis that monoecy arose twice (Fig. 5A), once in Calycophorae and once in Clade A. This is consistent with differences in the arrangements of male and female gonophores in the two clades. In Clade A, male and female zooids are found within the same cormidium (a single reiterated sequence of zooids along the stem, see Fig. 2). In these species, the male and female zooids are placed at very different but well defined locations within the cormidium. Meanwhile in calycophorans, each cormidium bears either male or female gonophores. In this form of monoecy, the male and female cormidia can either be in an alternating pattern, or there can be several male or female cormidia in a row. In either case, male and female zooids are found at the same corresponding locations within the cormidia. In sum, homoplasy in sexual system evolution along with variation in the spatial arrangement of gonophores within a colony suggest that siphonophores have evolved different ways to be monoecious. Both Calycophorae and Clade A have a large proportion of shallow water species (see section 3.7), suggesting that there may be an association between habitat depth and sexual mode. Similar independent transitions from gonochorism (separate sex) to hermaphrodism (both sexes in the same individual) have been identified in shallow-water scleractinian corals (Anthozoa, Cnidaria) [@kerr2011correlated]. To test this hypothesis, a more extensive taxon sampling of the Calycophorae is needed.

@@

![Stochastic mapping reconstruction of the evolutionary history of A) sexual mode, whether a colony is monoecious or dioecious and B) presence/absence of palpons (modified reduced gastrozooids). The color gradients show the reconstructed probability estimate of the discrete character states along the branches. Intermediate values reflect uncertainty.](figures/Figure5.pdf)

@@

\pagebreak

####SOWH analysis

@@

\pagebreak

#####Stochastic Character maps

```{r tentilla, echo=FALSE, message=F, warning=FALSE, verbose= FALSE, fig.width=6.5, fig.height=7, fig.cap= "Stochastic character map of presence of tentilla with *Physalia* included as not bearing tentilla."}
#Simmap TENTILLA
# plotTree(ultratree, lwd = 4)
# colors = c("black", "red")
# names(colors) = c("Absent", "Present")
# tentilla_sim %>% plotSimmap(lwd = 4, add = T,colors=colors)
# nodelabels(pie=(describe.simmap(tentilla_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
# add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
tentilla_obj <- densityMap(tentilla_sim,plot=FALSE)
tentilla_obj$cols[1:length(tentilla_obj$cols)]<-colorRampPalette(colors=c("#4A4ACC", "orange"), space="Lab")(length(tentilla_obj$cols))
plot(tentilla_obj)
```

```{r tentilla2, echo=FALSE, message=FALSE, warning=FALSE, verbose= FALSE, fig.width=6.5, fig.height=7, fig.cap= "Stochastic character map of presence of tentilla with *Physalia* included as bearing tentilla."}
#Simmap TENTILLA
# plotTree(ultratree, lwd = 4)
# colors = c("black", "red")
# names(colors) = c("Absent", "Present")
# tentilla_sim2 %>% plotSimmap(lwd = 4, add = T,colors=colors)
# nodelabels(pie=(describe.simmap(tentilla_sim2, plot=F)$ace) ,piecol=colors,cex=0.35)
# add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
tentilla2_obj <- densityMap(tentilla_sim2, plot=FALSE)
tentilla2_obj$cols[1:length(tentilla2_obj$cols)]<-colorRampPalette(colors=c("#4A4ACC", "orange"), space="Lab")(length(tentilla2_obj$cols))
plot(tentilla2_obj)
```

```{r nectosome, echo=FALSE, message=FALSE, warning=FALSE, verbose= FALSE,  fig.width=6.5, fig.height=7, fig.cap= "Stochastic character map of presence of nectosome."}
#Simmap NECTOSOME
# plotTree(ultratree, lwd = 4)
# colors = c("black", "red")
# names(colors) = c("Absent", "Present")
# nectosome_sim %>% plotSimmap(lwd = 4, add = T,colors=colors)
# nodelabels(pie=(describe.simmap(nectosome_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
# add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
nectosome_obj <- densityMap(nectosome_sim, plot=FALSE)
nectosome_obj$cols[1:length(nectosome_obj$cols)]<-colorRampPalette(colors=c("#4A4ACC", "orange"), space="Lab")(length(nectosome_obj$cols))
plot(nectosome_obj)
```

```{r desc_mantle, echo=FALSE, message=FALSE, warning=FALSE, verbose= FALSE, fig.width=6.5, fig.height=7, fig.cap= "Stochastic character map of presence of a descending mantle canal in the nectophores. Cystonects and Athorybia were excluded as they do not have a nectosome. "}
#Simmap Descending Mantle Canal
# plotTree(ultratree, lwd = 4)
# colors = c("black", "red")
# names(colors) = c("Absent", "Present")
# desc_mantle_sim %>% plotSimmap(lwd = 4, add = T,colors=colors)
# nodelabels(pie=(describe.simmap(desc_mantle_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
# add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
desc_mantle_obj <- densityMap(desc_mantle_sim, plot=FALSE)
desc_mantle_obj$cols[1:length(desc_mantle_obj$cols)]<-colorRampPalette(colors=c("#4A4ACC", "orange"), space="Lab")(length(desc_mantle_obj$cols))
plot(desc_mantle_obj)
```

```{r nectosome_pos, echo=FALSE, message=FALSE, warning=FALSE, verbose= FALSE, fig.width=6.5, fig.height=7, fig.cap= "Stochastic character map for the evolution of the position of the nectosome. Cystonects were excluded as they do not have a nectosome."}
#SIMMAP NectoPos
# plotTree(ultratree, lwd = 4)
# colors = c("black", "red")
# names(colors) = c("Dorsal", "Ventral")
# necto_pos_sim %>% plotSimmap(lwd = 4, add = T)
# nodelabels(pie=(describe.simmap(necto_pos_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
# add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
necto_pos_obj <- densityMap(necto_pos_sim, plot=FALSE)
necto_pos_obj$cols[1:length(necto_pos_obj$cols)]<-colorRampPalette(colors=c("#4A4ACC", "orange"), space="Lab")(length(necto_pos_obj$cols))
plot(necto_pos_obj)
```

```{r median_cont, echo=FALSE, message=FALSE, warning=FALSE, verbose= FALSE, fig.width=6.5, fig.height=7, fig.cap= "Brownian Motion character map of median depth of species observed with an MBARI ROV."}
depth_value = depth_median
depthmap <- contMap(dpruned_tree, depth_value, plot=F) %>% setMap(colors=c("cyan","blue","black"))
plot(depthmap)
```

```{r median_depth_extended, echo=FALSE, message=FALSE, warning=FALSE, verbose= FALSE, fig.width=6.5, fig.height=7, fig.cap= "Brownian Motion character map of median depth of species including blue water diving observations." }

#below are the model fit details

modelfit_white <- fitContinuous(ultratree, median_extended, model="white")$opt$aicc
modelfit_BM <- fitContinuous(ultratree, median_extended, model="BM")$opt$aicc
modelfit_OU <- fitContinuous(ultratree, median_extended, model="OU")$opt$aicc

@@

\pagebreak
